---
title: "worksheet4"
author: "Sunny Lee"
date: "2/10/2021"
output:
  pdf_document: default
  html_document: default
---

1)
a) A corr(X, Y) value of -.79 shows that X and Y are closely inversely correspondent/dependent.  

b) Since the correlation coefficient is close to zero, we find that X and Y are not very dependent in this case. 

c) corr(X, X) should be 1 since X should be perfectly depenedent with X. 

2)
a, b) 
```{r}
library("ggpubr")
credit <- read.csv("Credit.csv")

ggscatter(credit, x = "Cards", y = "Balance", add = "reg.line")

```
c)
From the above graph, we find that Balance does seem to be correlated with Cards, and there seems to be a positive correlation. 

d) 
```{r}
ggscatter(credit, x="Cards", y="Balance", add="reg.line", conf.int=TRUE)
```

e) 
The shaded region does look like it could capture a line with the $\hat{\beta_1} = 0$. One such line could be $\hat{\beta_0} = 500$, which would be a straight line only at $Balance = 500$ which looks like it could be contained in the shaded region. 

f)
```{r}
ggscatter(credit, x="Cards", y="Balance", add="reg.line", conf.int=TRUE, cor.coef=TRUE)
```

g) 
From what we have seen above, we can conclude that Cards is not a good predictor for Balance, as the p value is very low, and the shaded region does seem to contain a line where $\hat{\beta_1} = 0$