---
title: "homework3"
author: "Sunny Lee"
date: "2/14/2021"
output:
  pdf_document: default
---

1)
```{r}
library("MASS")
data("Boston")
```

2)
```{r}
?Boston
```
In this dataset, crim refers to the per capita crime rate by town. 

3) 
```{r}
crim01 <- rep(0, length(Boston$crim))
crim01[Boston$crim > median(Boston$crim)] <- 1
Boston <- data.frame(Boston, crim01)
```

4)
```{r}
cor(Boston)
tail(sort(abs(cor(Boston)[, 15])), 6)
```
Ignoring the crim01 variable, the five strongest predictors are tax, age, dis, rad, nox

5) 
```{r}
set.seed(5492)
v <- sort(sample(1:nrow(Boston),100)) # this creates a random selection of 100 numbers from 1 to n
Boston.test<-Boston[v,]
Boston.train<-Boston[-v,]
```

6)
```{r}
logreg.model <- glm(crim01~tax+age+dis+rad+nox, data = Boston.train, family = binomial)

logreg.prob <- predict(logreg.model, Boston.test, type = "response")
logreg.predict <- rep(0, length(logreg.prob))
logreg.predict[logreg.prob > .5] <- 1 

table(logreg.predict, Boston.test$crim01)
mean(logreg.predict == Boston.test$crim01)
mean(logreg.predict != Boston.test$crim01)
```
We find that the test error rate is 16 percent, and our test accuracy of our logisitc regression model is 84 percent

7) 
```{r}
lda.model <- lda(crim01~tax+age+dis+rad+nox, data = Boston.train)
lda.pred = predict(lda.model, Boston.test)

lda.class <- lda.pred$class

table(lda.class, Boston.test$crim01)
mean(lda.class == Boston.test$crim01)
mean(lda.class != Boston.test$crim01)
```

We find that the test error rate is 17 percent, and our test accuracy of our lda model is 83 percent. 

8)
```{r}
library(class)
set.seed(5492)

train.X <- cbind(Boston.train$tax, Boston.train$age, Boston.train$dis, Boston.train$rad, Boston.train$nox)
test.X <- cbind(Boston.test$tax, Boston.test$age, Boston.test$dis, Boston.test$rad, Boston.test$nox)
train.Y <- Boston.train$crim01

knn.pred <- knn(train.X, test.X, train.Y, k = 1)
table(knn.pred, Boston.test$crim01)
mean(knn.pred == Boston.test$crim01)
mean(knn.pred != Boston.test$crim01)
```

We find that hte test error rate is 8 percent and our test accuracy of our knn model is 92 percent. 